```{r Clear Workspace}
#Clear Workspace----
rm(list = ls())
```
---
title: "PLSR"
author: "Theodore Wiebold"
date: "October 30, 2019"
output:
  html_document:
    df_print: paged
---

```{r setup, include=FALSE}
#devtools::install_github("herveabdi/PTCA4CATA") # you only need this line of code if you haven't downloaded the #package
#install.packages("gridExtra")
#install.packages("ggplotify")
#install.packages("grid")
library(devtools)
library(ExPosition)
library(corrplot)
library(ggplot2)
library(PTCA4CATA)

# The following three functions allow you to arrange your plots in Rmarkdown
library(gridExtra)
library(ggplotify)
library(grid)

#install.packages('TExPosition')
#install.packages('ggplot2')
#install.packages('GGally')
#install.packages('CCA')
#install.packages('TInPosition')

library(InPosition)
# use the last version of PTCA
#devtools::install_github('HerveAbdi/PTCA4CATA')
#install.packages('gplots')
library(gplots)
#also install data4PCCAR last version
#devtools::install_github('HerveAbdi/data4PCCAR')
library(data4PCCAR)
library(tidyverse)

library('TExPosition')
library('ggplot2')
library('GGally')
library('CCA')
library('TInPosition')
```

#Data Cleaning----
```{r}
#Import data----
#Training Data-----
PHQ9 <- read.csv("~/Desktop/Experimental Psych/Depression and Memory Lab/PHQ9.csv", header = TRUE, sep = ",", quote="\"", row.names = NULL)
Beck <- read.csv("~/Desktop/Experimental Psych/Depression and Memory Lab/BAI.csv", header = TRUE, sep = ",", quote="\"", row.names = NULL)
SAM <- read.csv("~/Desktop/Experimental Psych/Depression and Memory Lab/SAM.csv", header = TRUE, sep = ",", quote="\"", row.names = NULL)
Demographics <- read.csv("~/Desktop/Experimental Psych/Depression and Memory Lab/Demographics.csv", header = TRUE, sep = ",", quote="\"", row.names = NULL)

#Testing Data----
TestData <- read.csv("~/Desktop/Experimental Psych/Depression and Memory Lab/Raw Data _Fall10.28.19.csv", header = TRUE, sep = ",", quote="\"", row.names = NULL)
TestData <- TestData[(nrow(PHQ9) +1):nrow(TestData),]


PHQ9 <- PHQ9[,c(-11,-12)] #removes life question and if they continued
Beck <- Beck[,-1] #removes id
SAM <- SAM[,-1] #removed id
Demographics <- Demographics[, -c(1:5, 7:12, 20)] #removes test taking information
DemographicsTest <- TestData[,c(1:20)]
TestData <- TestData[,-c(1:20)] #removes demographic questions
PHQ9Test <- TestData[,c(1:9)]
TestData <- TestData[,-c(1:15)] #removes PHQ9
BeckTest <- TestData[,c(1:10, (ncol(TestData)-10):ncol(TestData))]
TestData <- TestData[,-c(1:10)]
SAMTest <- TestData[, c(34:59)]

#Training Set
AllParticipants <- cbind2(PHQ9,Beck)
AllParticipants <- cbind2(AllParticipants, Demographics)
AllParticipants <- cbind2(AllParticipants, SAM)
rawAllParticipants <- nrow(AllParticipants) #shows number of observations from raw dataset

#Test Set
AllParticipantsTest <- cbind2(PHQ9Test,BeckTest)
AllParticipantsTest <- cbind2(AllParticipantsTest, DemographicsTest)
AllParticipantsTest <- cbind2(AllParticipantsTest, SAMTest)
rawAllParticipantsTest <- nrow(AllParticipantsTest) #shows number of observations from raw dataset

#Remove rows with missing data----
#PHQ9 <- na.omit(PHQ9) #omits rows with no values
#naomitPHQ9 <- nrow(PHQ9) #shows number of observations from naomit data
#naomitPHQ9 <- rawPHQ9 - naomitPHQ9 #shows number of observations removed 
#Beck <- na.omit(Beck) #omits rows with no values
#naomitBeck <- nrow(Beck) #shows number of observations from naomit data
#naomitBeck <- rawBeck - naomitBeck #shows number of observations removed 

#Training Data
AllParticipants <- na.omit(AllParticipants) #omits rows with no values
naomitAllParticipants <- nrow(AllParticipants) #shows number of observations from naomit data
naomitAllParticipants <- rawAllParticipants - naomitAllParticipants #shows number of observations removed

#Testing Data
AllParticipantsTest <- na.omit(AllParticipantsTest) #omits rows with no values
naomitAllParticipantsTest <- nrow(AllParticipantsTest) #shows number of observations from naomit data
naomitAllParticipantsTest <- rawAllParticipantsTest - naomitAllParticipantsTest #shows number of observations removed

#Remove duplicates PHQ9----
#n_occurWithDuplicatesPHQ9 <- data.frame(table(PHQ9$id)) #gives a dataframe of how many times each id occured in the data
#NumberOfDubplicatesPHQ9 <- sum(n_occurWithDuplicatesPHQ9$Freq-1) #gives the number of duplicates
 #for (i in 1:NumberOfDubplicatesPHQ9) { #for-loop removing duplicates
 #i <- anyDuplicated(PHQ9$id)
 #PHQ9 <- PHQ9[-i,]
  # }
#n_occurNoDuplicatesPHQ9 <- data.frame(table(PHQ9$id))  #shows there are no duplicates reamining

#Remove duplicates Beck----
#n_occurWithDuplicatesBeck <- data.frame(table(Beck$id)) #gives a dataframe of how many times each id occured in the data
#NumberOfDubplicatesBeck <- sum(n_occurWithDuplicatesBeck$Freq-1) #gives the number of duplicates
 #for (j in 1:NumberOfDubplicatesBeck) { #for-loop removing duplicates
 #j <- anyDuplicated(Beck$id)
 #Beck <- Beck[-j,]
  # }
#n_occurNoDuplicatesBeck <- data.frame(table(Beck$id))  #shows there are no duplicates reamining


#Remove duplicates AllParticipants----
n_occurWithDuplicatesAll <- data.frame(table(AllParticipants$id)) #gives a dataframe of how many times each id occured in the data
NumberOfDubplicatesAll <- sum(n_occurWithDuplicatesAll$Freq-1) #gives the number of duplicates
 for (j in 1:NumberOfDubplicatesAll) { #for-loop removing duplicates
 j <- anyDuplicated(AllParticipants$id)
 AllParticipants <- AllParticipants[-j,]
   }
n_occurNoDuplicatesAll <- data.frame(table(AllParticipants$id))  #shows there are no duplicates reamining

#Remove duplicates AllParticipantsTest----
n_occurWithDuplicatesAllTest <- data.frame(table(AllParticipantsTest$id)) #gives a dataframe of how many times each id occured in the data
#NumberOfDubplicatesAll <- sum(n_occurWithDuplicatesAll$Freq-1) #gives the number of duplicates
 #for (j in 1:NumberOfDubplicatesAll) { #for-loop removing duplicates
 #j <- anyDuplicated(AllParticipantsTest$id)
 #AllParticipantsTest <- AllParticipantsTest[-j,]
   #}
#n_occurNoDuplicatesAll <- data.frame(table(AllParticipantsTest$id))  #shows there are no duplicates reamining

#Remove columns and rows with string identifiers----
#AllParticipants <- AllParticipants[,-12] #Removes second id column
#AllParticipants <- AllParticipants[c(-1,-2),] #removes row of questions and import id

#Convert character to numeric in all columns----
AllParticipants[ , c(1:ncol(AllParticipants))] <- apply(AllParticipants[ , c(1:ncol(AllParticipants))], 2, function(x) as.numeric(as.character(x)))

AllParticipantsTest[ , c(1:ncol(AllParticipantsTest))] <- apply(AllParticipantsTest[ , c(1:ncol(AllParticipantsTest))], 2, function(x) as.numeric(as.character(x)))

#Training sets----
PHQ9 <- AllParticipants[,2:10]
Beck <- AllParticipants[,11:31]
Demographics <- AllParticipants[,32:47]
SAM <- AllParticipants[,48:73]
SAMEpisodic <- SAM[,1:8]
SAMSemantic <- SAM[,9:14]
SAMSpatial <- SAM[,15:20]
SAMFuture <- SAM[,21:26]


#Test Sets----
PHQ9Test <- AllParticipantsTest[,c(1:9)]
BeckTest <- AllParticipantsTest[,c(10:30)]
SAMEpisodicTest <- AllParticipantsTest[,c(51:58)]


#Reverse code questions 1 and 2
for (b in 1:2) {
  SAMEpisodic[,b] <- (max(SAMEpisodic) +1 ) - SAMEpisodic[,b]
 SAMEpisodicTest[,b] <- (max(SAMEpisodicTest) +1 ) - SAMEpisodicTest[,b]
}

```

#Create Variable groups
```{r}
#Make key words as each variable representing each question in PHQ9----
colnames(PHQ9) <- c('Pleasure','Hopeless','Sleep','Energy','Appetite','Failure','Focus','Speed','Suicide')
rownames(PHQ9) <-c(1:nrow(PHQ9))

colnames(PHQ9Test) <- c('Pleasure','Hopeless','Sleep','Energy','Appetite','Failure','Focus','Speed','Suicide')
rownames(PHQ9Test) <-c(1:nrow(PHQ9Test))

#Make key words as each variable representing each question in Beck----
colnames(Beck) <- c('Numbness','Hot','Wobbly','Tense','Fear','Dizzy','Heart','Unsteady','Terrified','Nervous', 'Choking', 'Trembling', 'Shaky', 'Control', 'Breathing', 'Dying', 'Scared', 'Indigestion', 'Faint', 'Flushed', 'Sweats')
rownames(Beck) <-c(1:nrow(Beck))

colnames(BeckTest) <- c('Numbness','Hot','Wobbly','Tense','Fear','Dizzy','Heart','Unsteady','Terrified','Nervous', 'Choking', 'Trembling', 'Shaky', 'Control', 'Breathing', 'Dying', 'Scared', 'Indigestion', 'Faint', 'Flushed', 'Sweats')
rownames(BeckTest) <-c(1:nrow(BeckTest))

#Make key words as each variable representing each question in SAMEpisodic----
colnames(SAMEpisodic) <- c("Specific", "Order", "Object", "Wearing", "Confidence", "Many", "Day", "People")
rownames(SAMEpisodic) <-c(1:nrow(SAMEpisodic))

colnames(SAMEpisodicTest) <- c("Specific", "Order", "Object", "Wearing", "Confidence", "Many", "Day", "People")
rownames(SAMEpisodicTest) <-c(1:nrow(SAMEpisodicTest))

#Convert character to numeric in all columns----
PHQ9[ , c(1:ncol(PHQ9))] <- apply(PHQ9[ , c(1:ncol(PHQ9))], 2, function(x) as.numeric(as.character(x)))

PHQ9Test[ , c(1:ncol(PHQ9Test))] <- apply(PHQ9Test[ , c(1:ncol(PHQ9Test))], 2, function(x) as.numeric(as.character(x)))

Beck[ , c(1:ncol(Beck))] <- apply(Beck[ , c(1:ncol(Beck))], 2, function(x) as.numeric(as.character(x)))

BeckTest[ , c(1:ncol(BeckTest))] <- apply(BeckTest[ , c(1:ncol(BeckTest))], 2, function(x) as.numeric(as.character(x)))

SAMEpisodic[ , c(1:ncol(SAMEpisodic))] <- apply(SAMEpisodic[ , c(1:ncol(SAMEpisodic))], 2, function(x) as.numeric(as.character(x)))

SAMEpisodicTest[ , c(1:ncol(SAMEpisodicTest))] <- apply(SAMEpisodicTest[ , c(1:ncol(SAMEpisodicTest))], 2, function(x) as.numeric(as.character(x)))

#Creat grouping based on Depression Severity----
ColumnsPHQ9 <- length(PHQ9)
totalscorePHQ9 <- rowSums(PHQ9[,1:ColumnsPHQ9]) 
for (i in 1:length(totalscorePHQ9)){
severity <- totalscorePHQ9[i]
  if (severity <= 4){
  totalscorePHQ9[i] <- 1 #Minimal depression
  }
  if (severity > 4 & severity <= 9){
  totalscorePHQ9[i] <- 2 #Mild depression
  }
  if (severity > 9 & severity <= 14){
  totalscorePHQ9[i] <- 3 #Moderate depression
  }
  if (severity > 14 & severity <= 19){
  totalscorePHQ9[i] <- 4 #Moderately severe depression
  }
  if (severity >19){
  totalscorePHQ9[i] <- 5 #Severe depression
  }
}

#Creat grouping based on Anxiety Severity----
ColumnsBeck <- length(Beck)
totalscoreBeck <- rowSums(Beck[,1:ColumnsBeck]) 
for (i in 1:length(totalscoreBeck)){
severityAnxiety <- totalscoreBeck[i]
  if (severityAnxiety <= 21){
  totalscoreBeck[i] <- 1 #Low Anxiety
  }
  if (severityAnxiety > 21 & severityAnxiety <= 35){
  totalscoreBeck[i] <- 2 #Moderate Anxiety
  }
  if (severityAnxiety > 35){
  totalscoreBeck[i] <- 3 #Concerning levels of Anxiety
  }
}

BothTrain <- cbind(PHQ9, Beck)
BothTest <- cbind(PHQ9Test, BeckTest)
```


## Data set: PHQ 
It measures the 9 different beers (rows) on 30 beer characteristics (columns).

```{r data_set}
#Training sets----
head(PHQ9, n = 6L)
head(Beck, n = 6L)
head(SAMEpisodic, n = 6L)

#Test sets----
head(PHQ9Test, n = 6L)
head(BeckTest, n =6L)
head(SAMEpisodicTest, n = 6L)
```

#Covariance Plots
```{r}

# Compute the covariance matrix----
XY.corPB <- cov(PHQ9,Beck)
# Plot it with corrplot
corrplot(XY.corPB, method = "color")

XY.corPS <- cov(PHQ9,SAMEpisodic)
# Plot it with corrplot
corrplot(XY.corPS, method = "color")

XY.corBS <- cov(Beck,SAMEpisodic)
# Plot it with corrplot
corrplot(XY.corBS, method = "color")
```

# Analysis
```{r}
#install.packages('pls')
library('pls')

#Change for formula
SAMEpisodicResponse <- as.matrix(SAMEpisodic)
PHQ9Terms <- as.matrix(PHQ9)
BeckTerms <- as.matrix(Beck)
BothTerms <- as.matrix(BothTrain)

#PLSRs Training
resPLSRps <- plsr(SAMEpisodicResponse ~ PHQ9Terms, ncomp = ncol(PHQ9), data = PHQ9, validation = "LOO")
resPLSRbs <- plsr(SAMEpisodicResponse ~ BeckTerms, ncomp = ncol(Beck), data = Beck, validation = "LOO")
resPLSRboths <- plsr(SAMEpisodicResponse ~ BothTerms, ncomp = ncol(BothTrain), data = BothTrain, validation = "LOO")

#PLSRs Testing
resPLSRpsRobust <- RMSEP(resPLSRps, newdata = PHQ9Test)
resPLSRbsRobust <- RMSEP(resPLSRbs, newdata = BeckTest)
resPLSRbothsRobust <- RMSEP(resPLSRboths, newdata = BothTest)
```

#Scree Plot
```{r}
PlotScree(ev = explvar(resPLSRps),
               plotKaiser = TRUE,
               title = "PLSR PHQ9 and SAM Episodic Explained Variance per Dimension")

PlotScree(ev = explvar(resPLSRbs),
               plotKaiser = TRUE,
               title = "PLSR Beck and SAM Episodic Explained Variance per Dimension")

PlotScree(ev = explvar(resPLSRboths),
               plotKaiser = TRUE,
               title = "PLSR PHQ9/Beck and SAM Episodic Explained Variance per Dimension")

```

#Crossvalidation Predictions
```{r}
#PHQ9 and SAM Episodic
plot(resPLSRps, ncomp = 1, asp = 1, line = TRUE)

#Beck and SAM Episodic
plot(resPLSRbs, ncomp = 1, asp = 1, line = TRUE)

#Both PHQ9 and Beck on SAM Episodic
plot(resPLSRboths, ncomp = 2, asp = 1, line = TRUE)
```


###Weights 
```{r row factor scores}
#Weights PHQ9
PHQ9Colors <- prettyGraphsColorSelection(n.colors = ncol(PHQ9))
###### 1 ====
ctri <- resPLSRps$loading.weights
# BR1
c001.plotCtrP.1 <- PrettyBarPlot2(
                       bootratio = round(100*ctri[,1]), 
                       threshold = 100 / nrow(ctri), 
                       ylim = NULL, 
                       color4bar = gplots::col2hex(PHQ9Colors),
                       color4ns = "gray75", 
                       plotnames = TRUE, 
                       main = 'PHQ9 Weights Dim 1.', 
                       ylab = "Signed Contributions")
#_____________________________________________________________________
###### 2 ====
# 
c002.plotCtrP.2 <- PrettyBarPlot2(
  bootratio = round(100*ctri[,2]), 
  threshold = 100 / nrow(ctri), 
  ylim = NULL, 
  color4bar = gplots::col2hex(PHQ9Colors),
  color4ns = "gray75", 
  plotnames = TRUE, 
  main = 'PHQ9 Weights Dim 2.', 
  ylab = "Signed Contributions")

#Weights Beck
BeckColors <- prettyGraphsColorSelection(n.colors = ncol(Beck))
###### 1 ====
ctri2 <- resPLSRbs$loading.weights
# BR1
c001.plotCtrB.1 <- PrettyBarPlot2(
                       bootratio = round(100*ctri2[,1]), 
                       threshold = 100 / nrow(ctri2), 
                       ylim = NULL, 
                       color4bar = gplots::col2hex(BeckColors),
                       color4ns = "gray75", 
                       plotnames = TRUE, 
                       main = 'Beck Weights Dim 1.', 
                       ylab = "Signed Contributions")
#_____________________________________________________________________
###### 2 ====
# 
c002.plotCtrB.2 <- PrettyBarPlot2(
  bootratio = round(100*ctri2[,2]), 
  threshold = 100 / nrow(ctri2), 
  ylim = NULL, 
  color4bar = gplots::col2hex(BeckColors),
  color4ns = "gray75", 
  plotnames = TRUE, 
  main = 'Beck Weights Dim 2.', 
  ylab = "Signed Contributions")

#Weights Both
BothColors <- matrix(,ncol = 30)
BothColors[,1:9] <- "mediumorchid4"
BothColors[,10:30] <- "olivedrab3"
###### 1 ====
ctri2 <- resPLSRboths$loading.weights
# BR1
c001.plotCtrBoth.1 <- PrettyBarPlot2(
                       bootratio = round(100*ctri2[,1]), 
                       threshold = 100 / nrow(ctri2), 
                       ylim = NULL, 
                       color4bar = gplots::col2hex(BothColors),
                       color4ns = "gray75", 
                       plotnames = TRUE, 
                       main = 'Both Weights Dim 1.', 
                       ylab = "Signed Contributions")
#_____________________________________________________________________
###### 2 ====
# 
c002.plotCtrBoth.2 <- PrettyBarPlot2(
  bootratio = round(100*ctri2[,2]), 
  threshold = 100 / nrow(ctri2), 
  ylim = NULL, 
  color4bar = gplots::col2hex(BothColors),
  color4ns = "gray75", 
  plotnames = TRUE, 
  main = 'Both Weights Dim 2.', 
  ylab = "Signed Contributions")

  grid.arrange(
    as.grob(c001.plotCtrP.1),
    as.grob(c002.plotCtrP.2),
    ncol = 2,nrow = 1,
    top = textGrob("Contributions", gp = gpar(fontsize = 18, font = 3))
  )
BothWeightsPHQ9 <- recordPlot() # you need this line to be able to save them in the end

  grid.arrange(
    as.grob(c001.plotCtrB.1),
    as.grob(c002.plotCtrB.2),
    ncol = 2,nrow = 1,
    top = textGrob("Contributions", gp = gpar(fontsize = 18, font = 3))
  )
BothWeightsBeck <- recordPlot() # you need this line to be able to save them in the end

  grid.arrange(
    as.grob(c001.plotCtrBoth.1),
    as.grob(c002.plotCtrBoth.2),
    ncol = 2,nrow = 1,
    top = textGrob("Contributions", gp = gpar(fontsize = 18, font = 3))
  )
BothWeightsBoth <- recordPlot() # you need this line to be able to save them in the end
```


# Latent Variables
```{r}
#Latent Variables of PHQ9
plot.lv1 <- createFactorMap(resPLSRps$scores[,1:2],
                            title = "Latent Variables of PHQ9",
                         col.points = "mediumorchid4",
                         col.labels = "mediumorchid4",
                         display.labels = FALSE,
                         alpha.points = 0.2
                         )

plot1 <- plot.lv1$zeMap_background + plot.lv1$zeMap_dots
plot1

#Latent Variables of Beck
plot.lv2 <- createFactorMap(resPLSRbs$scores[,1:2],
                            title = "Latent Variables of Beck",
                         col.points = "olivedrab3",
                         col.labels = "olivedrab3",
                         display.labels = FALSE,
                         alpha.points = 0.2
                         )

plot2 <- plot.lv2$zeMap_background + plot.lv2$zeMap_dots
plot2

#Latent Variables of Both
plot.lv3 <- createFactorMap(resPLSRboths$scores[,1:2],
                            title = "Latent Variables of Both",
                         col.points = "royalblue",
                         col.labels = "royalblue",
                         display.labels = FALSE,
                         alpha.points = 0.2
                         )

plot3 <- plot.lv3$zeMap_background + plot.lv3$zeMap_dots
plot3
```



#Root Mean Square Error of Prediction Comparisons
```{r}
#Standard deviations of the residuals from the regression line i.e. how clustered the predicted data pionts are around the line of best fit
PHQ9TrainPlot <- plot(RMSEP(resPLSRps),main = 'PHQ9 Train')
PHQ9TestPlot <- plot(resPLSRpsRobust, main = "PHQ9 Test")

BeckTrainPlot <- plot(RMSEP(resPLSRbs),main = 'Beck Train')
BeckTestPlot <- plot(resPLSRbsRobust, main = "Beck Test")

BothTrainPlot <- plot(RMSEP(resPLSRboths),main = 'Both Train')
BothTestPlot <- plot(resPLSRbothsRobust, main = "Both Test")
```

# Correlation Between Predicted and Observed Scores
```{r}
detach("package:pls", unload=TRUE)

#Correlation of PHQ9 predicted SAM Episdoic with observed SAM Episodic
XY.corPB <- cor(resPLSRps$validation$pred[,,1],SAMEpisodic)
# Plot it with corrplot
corrplot(XY.corPB, method = "number", addCoefasPercent = TRUE)

#Correlation of Beck predicted SAM Episdoic with observed SAM Episodic
XY.corPB <- cor(resPLSRbs$validation$pred[,,1],SAMEpisodic)
# Plot it with corrplot
corrplot(XY.corPB, method = "number", addCoefasPercent = TRUE)

#Correlation of Both predicted SAM Episdoic with observed SAM Episodic
XY.corPB <- cor(resPLSRboths$validation$pred[,,2],SAMEpisodic)
# Plot it with corrplot
corrplot(XY.corPB, method = "number", addCoefasPercent = TRUE)
```


## Summary

When we interpret the factor scores and latent variables, the PLSR revealed:

Number of components:

PHQ9: only 1 was above the Kaiser line

Beck: only 1 was above the Kaiser line

Both: 2 were above the Kaiser line

RMSEP:

All error of predictions were a little bit above one standard deviation. However, this is Likert scale data (ordinal) so it is difficult to determine what 1 SD is. 

There didn't seem to be much difference between the testing and training data meaning the predictions are able to be generalized. 

Covariance Plots:

After recoding the 1st and 2nd question in the SAM Episodic portion, it seems that a PLSC may reveal that higher scores on Beck and PHQ9 are associated with lower scores on the SAM Episodic!



