```{r Clear Workspace}
#Clear Workspace----
rm(list = ls())
```
---
title: "RGCCA"
author: "Theodore Wiebold"
date: "October 22, 2019"
output:
  html_document:
    df_print: paged
---

```{r setup, include=FALSE}
#devtools::install_github("herveabdi/PTCA4CATA") # you only need this line of code if you haven't downloaded the #package
#install.packages("gridExtra")
#install.packages("ggplotify")
#install.packages("grid")
library(devtools)
library(ExPosition)
library(corrplot)
library(ggplot2)
library(PTCA4CATA)
#devtools::install_github('HerveAbdi/data4PCCAR')
library(data4PCCAR)
library(tidyverse)

# The following three functions allow you to arrange your plots in Rmarkdown
library(gridExtra)
library(ggplotify)
library(grid)
library(gplots)

#install.packages('TExPosition')
#install.packages('ggplot2')
#install.packages('GGally')
#install.packages('CCA')
#install.packages('TInPosition')

library('TExPosition')
library('ggplot2')
library('GGally')
library('CCA')
library('TInPosition')

#install.packages("RGCCA")
library(RGCCA)
```

#Data Cleaning----
```{r}
#Data Cleaning----

#Import data----
PHQ9 <- read.csv("~/Desktop/Experimental Psych/Depression and Memory Lab/PHQ9.csv", header = TRUE, sep = ",", quote="\"", row.names = NULL)
Beck <- read.csv("~/Desktop/Experimental Psych/Depression and Memory Lab/BAI.csv", header = TRUE, sep = ",", quote="\"", row.names = NULL)
SAM <- read.csv("~/Desktop/Experimental Psych/Depression and Memory Lab/SAM.csv", header = TRUE, sep = ",", quote="\"", row.names = NULL)
Demographics <- read.csv("~/Desktop/Experimental Psych/Depression and Memory Lab/Demographics.csv", header = TRUE, sep = ",", quote="\"", row.names = NULL)

PHQ9 <- PHQ9[,c(-11,-12)] #removes life question and if they continued
Beck <- Beck[,-1] #removes id
SAM <- SAM[,-1] #removed id
Demographics <- Demographics[, -c(1:5, 7:12, 20)] #removes test taking information

AllParticipants <- cbind2(PHQ9,Beck)
AllParticipants <- cbind2(AllParticipants, Demographics)
AllParticipants <- cbind2(AllParticipants, SAM)
rawAllParticipants <- nrow(AllParticipants) #shows number of observations from raw dataset

#Remove rows with missing data----
#PHQ9 <- na.omit(PHQ9) #omits rows with no values
#naomitPHQ9 <- nrow(PHQ9) #shows number of observations from naomit data
#naomitPHQ9 <- rawPHQ9 - naomitPHQ9 #shows number of observations removed 
#Beck <- na.omit(Beck) #omits rows with no values
#naomitBeck <- nrow(Beck) #shows number of observations from naomit data
#naomitBeck <- rawBeck - naomitBeck #shows number of observations removed 

AllParticipants <- na.omit(AllParticipants) #omits rows with no values
naomitAllParticipants <- nrow(AllParticipants) #shows number of observations from naomit data
naomitAllParticipants <- rawAllParticipants - naomitAllParticipants #shows number of observations removed

#Remove duplicates PHQ9----
#n_occurWithDuplicatesPHQ9 <- data.frame(table(PHQ9$id)) #gives a dataframe of how many times each id occured in the data
#NumberOfDubplicatesPHQ9 <- sum(n_occurWithDuplicatesPHQ9$Freq-1) #gives the number of duplicates
 #for (i in 1:NumberOfDubplicatesPHQ9) { #for-loop removing duplicates
 #i <- anyDuplicated(PHQ9$id)
 #PHQ9 <- PHQ9[-i,]
  # }
#n_occurNoDuplicatesPHQ9 <- data.frame(table(PHQ9$id))  #shows there are no duplicates reamining

#Remove duplicates Beck----
#n_occurWithDuplicatesBeck <- data.frame(table(Beck$id)) #gives a dataframe of how many times each id occured in the data
#NumberOfDubplicatesBeck <- sum(n_occurWithDuplicatesBeck$Freq-1) #gives the number of duplicates
 #for (j in 1:NumberOfDubplicatesBeck) { #for-loop removing duplicates
 #j <- anyDuplicated(Beck$id)
 #Beck <- Beck[-j,]
  # }
#n_occurNoDuplicatesBeck <- data.frame(table(Beck$id))  #shows there are no duplicates reamining

#Remove duplicates AllParticipants----
n_occurWithDuplicatesAll <- data.frame(table(AllParticipants$id)) #gives a dataframe of how many times each id occured in the data
NumberOfDubplicatesAll <- sum(n_occurWithDuplicatesAll$Freq-1) #gives the number of duplicates
 for (j in 1:NumberOfDubplicatesAll) { #for-loop removing duplicates
 j <- anyDuplicated(AllParticipants$id)
 AllParticipants <- AllParticipants[-j,]
   }
n_occurNoDuplicatesAll <- data.frame(table(AllParticipants$id))  #shows there are no duplicates reamining

#Remove columns and rows with string identifiers----
#AllParticipants <- AllParticipants[,-12] #Removes second id column
#AllParticipants <- AllParticipants[c(-1,-2),] #removes row of questions and import id

#Convert character to numeric in all columns----
AllParticipants[ , c(1:ncol(AllParticipants))] <- apply(AllParticipants[ , c(1:ncol(AllParticipants))], 2, function(x) as.numeric(as.character(x)))

PHQ9 <- AllParticipants[,2:10]
Beck <- AllParticipants[,11:31]
Demographics <- AllParticipants[,32:47]
SAM <- AllParticipants[,48:73]
SAMEpisodic <- SAM[,1:8]
SAMSemantic <- SAM[,9:14]
SAMSpatial <- SAM[,15:20]
SAMFuture <- SAM[,21:26]
```

## Create groups of PHQ9 and Beck

```{r}
#Make key words as each variable representing each question in PHQ9----
colnames(PHQ9) <- c('Pleasure','Hopeless','Sleep','Energy','Appetite','Failure','Focus','Speed','Suicide')
rownames(PHQ9) <-c(1:nrow(PHQ9))

#Make key words as each variable representing each question in Beck----
colnames(Beck) <- c('Numbness','Hot','Wobbly','Tense','Fear','Dizzy','Heart','Unsteady','Terrified','Nervous', 'Choking', 'Trembling', 'Shaky', 'Control', 'Breathing', 'Dying', 'Scared', 'Indigestion', 'Faint', 'Flushed', 'Sweats')
rownames(Beck) <-c(1:nrow(Beck))

#Make key words as each variable representing each question in SAMEpisodic----
colnames(SAMEpisodic) <- c("Specific", "Order", "Object", "Wearing", "Confidence", "Many", "Day", "People")
rownames(SAMEpisodic) <-c(1:nrow(SAMEpisodic))


#Convert character to numeric in all columns----
PHQ9[ , c(1:ncol(PHQ9))] <- apply(PHQ9[ , c(1:ncol(PHQ9))], 2, function(x) as.numeric(as.character(x)))

Beck[ , c(1:ncol(Beck))] <- apply(Beck[ , c(1:ncol(Beck))], 2, function(x) as.numeric(as.character(x)))

SAMEpisodic[ , c(1:ncol(SAMEpisodic))] <- apply(SAMEpisodic[ , c(1:ncol(SAMEpisodic))], 2, function(x) as.numeric(as.character(x)))

#Creat grouping based on Depression Severity----
ColumnsPHQ9 <- length(PHQ9)
totalscorePHQ9 <- rowSums(PHQ9[,1:ColumnsPHQ9]) 
for (i in 1:length(totalscorePHQ9)){
severity <- totalscorePHQ9[i]
  if (severity <= 4){
  totalscorePHQ9[i] <- 1 #Minimal depression
  }
  if (severity > 4 & severity <= 9){
  totalscorePHQ9[i] <- 2 #Mild depression
  }
  if (severity > 9 & severity <= 14){
  totalscorePHQ9[i] <- 3 #Moderate depression
  }
  if (severity > 14 & severity <= 19){
  totalscorePHQ9[i] <- 4 #Moderately severe depression
  }
  if (severity >19){
  totalscorePHQ9[i] <- 5 #Severe depression
  }
}

#Creat grouping based on Anxiety Severity----
ColumnsBeck <- length(Beck)
totalscoreBeck <- rowSums(Beck[,1:ColumnsBeck]) 
for (i in 1:length(totalscoreBeck)){
severityAnxiety <- totalscoreBeck[i]
  if (severityAnxiety <= 21){
  totalscoreBeck[i] <- 1 #Low Anxiety
  }
  if (severityAnxiety > 21 & severityAnxiety <= 35){
  totalscoreBeck[i] <- 2 #Moderate Anxiety
  }
  if (severityAnxiety > 35){
  totalscoreBeck[i] <- 3 #Concerning levels of Anxiety
  }
}

#Reverse code questions 1 and 2
for (b in 1:2) {
  SAMEpisodic[,b] <- (max(SAMEpisodic) +1 ) - SAMEpisodic[,b]
}

```

## Data set: PHQ 
It measures the 9 different beers (rows) on 30 beer characteristics (columns).

```{r data_set}
head(Beck, n = 6L)
head(PHQ9, n = 6L)
head(SAM, n = 6L)
head(Demographics, n = 6L)
```

#Covariance and Correlation Plots
```{r}
#Beck----
cov.plot.dataBeck <-cov(Beck)
diag(cov.plot.dataBeck) <- 1
cov.plot.numBeck <- corrplot(cov.plot.dataBeck, method = "number", type = "upper", tl.pos = "lt",
                        tl.cex = .7, tl.srt = 45, addCoefasPercent = TRUE, number.cex = .7)
cov.plot.fullBeck <- corrplot(cov.plot.dataBeck, method = "ellipse", type = "lower", add = TRUE,
                          diag = FALSE, tl.pos = "n", cl.pos = "n")
#PHQ9----
cov.plot.dataPHQ9 <-cov(PHQ9)
diag(cov.plot.dataPHQ9) <- 1
cov.plot.numPHQ9 <- corrplot(cov.plot.dataPHQ9, method = "number", type = "upper", tl.pos = "lt",
                        tl.cex = .7, tl.srt = 45, addCoefasPercent = TRUE)
cov.plot.fullPHQ9 <- corrplot(cov.plot.dataPHQ9, method = "ellipse", type = "lower", add = TRUE,
                          diag = FALSE, tl.pos = "n", cl.pos = "n")

#SAM----
cor.plot.dataSAM <-cor(SAMEpisodic)
#diag(cor.plot.dataSAM) <- 1
cor.plot.numSAM <- corrplot(cor.plot.dataSAM, method = "number", type = "upper", tl.pos = "lt",
                        tl.cex = .7, tl.srt = 45, addCoefasPercent = TRUE)
cor.plot.fullSAM <- corrplot(cor.plot.dataSAM, method = "ellipse", type = "lower", add = TRUE,
                          diag = FALSE, tl.pos = "n", cl.pos = "n")

#Diagonals are all ones because some of the variances were above 1 and corrplot does not except values outside [-1,1]
#CREDIT GOES TO SHELIA!!!

#Covariance of PHQ9 and Beck
cov.plot.dataBoth <-cov(PHQ9, Beck)
#diag(cov.plot.dataPHQ9) <- 1
cov.plot.numBoth <- corrplot(cov.plot.dataBoth, method = "number", type = "full", tl.pos = "lt", number.cex = 1, tl.cex = .9, tl.srt = 45, addCoefasPercent = TRUE)
#cor.plot.fullBoth <- corrplot(cor.plot.dataBoth, method = "ellipse", type = "lower", add = TRUE,
                          #diag = FALSE, tl.pos = "n", cl.pos = "n")

#Correlation between PHQ9 and SAM
cor.plot.dataPS <-cor(PHQ9, SAMEpisodic)
cor.plot.numPS <- corrplot(cor.plot.dataPS, method = "number", type = "full", tl.pos = "lt", number.cex = 1, tl.cex = .9, tl.srt = 45, addCoefasPercent = TRUE)

#Correlation between Beck and SAM
cor.plot.dataBS <-cor(Beck, SAMEpisodic)
cor.plot.numBS <- corrplot(cor.plot.dataBS, method = "number", type = "full", tl.pos = "lt", number.cex = 1, tl.cex = .9, tl.srt = 45, addCoefasPercent = TRUE)
```

# Analysis
```{r}
resPCAinferencePHQ9 <- epPCA.inference.battery(PHQ9, scale = FALSE, DESIGN = totalscorePHQ9, graphs = FALSE)

resPCAinferenceBeck <- epPCA.inference.battery(Beck, scale = FALSE, DESIGN = totalscoreBeck, graphs = FALSE)

resPCAinferenceSAMEpisodic <- epPCA.inference.battery(SAMEpisodic, scale = FALSE, graphs = FALSE)

Blocks <- list(PHQ9, Beck, SAMEpisodic)
ComponentsFixed <- matrix(c(4,4,1), 1, 3)
ComponentsExplore <- matrix(c(2,2,2), 1, 3)
C <- 1-diag(3)

resRGCCA <- rgcca(Blocks, C, tau = "optimal", ncomp = ComponentsExplore,  scheme = "horst", scale = TRUE) 
resRGCCA$tau
#tau = shrinkage parameter e.g. choice between [0,1] where 0 = correlation and 1 = covariance
#scheme = horst or g(x) = x makes objective function convex with this inner-weighting scheme i.e. how the blocks are weighted
#C = relationship between all blocks [0,1] where 0 means they are not connect and 1 means they are e.g. in this design all blocks are connected

```

#Screeplots
```{r}
scree.PHQ9 <- PlotScree(ev = resRGCCA$AVE$AVE_X[[1]],
               plotKaiser = TRUE,
               title = "PHQ9 Explained Average Explained Variance per Dimension")

scree.Beck <- PlotScree(ev = resRGCCA$AVE$AVE_X[[2]],
               plotKaiser = TRUE,
               title = "Beck Explained Average Explained Variance per Dimension")

scree.SAMEpisodic <- PlotScree(ev = resRGCCA$AVE$AVE_X[[3]],
               plotKaiser = TRUE,
               title = "SAM Episodic Average Explained Variance per Dimension")
```

#Correlation Plots
```{r}
#devtools::install_github("kassambara/ggpubr")
library("ggpubr")

#PHQ9 and Beck correlation of Row Factor Scores of comp 1
PHQ9Beck <- cbind(data.frame(resRGCCA$Y[[1]][,1]), data.frame(resRGCCA$Y[[2]][,1]))
colnames(PHQ9Beck) <- c("PHQ9","Beck")

PHQ9BeckScatter <- ggscatter(PHQ9Beck, x = "PHQ9", y = "Beck", 
          add = "reg.line", conf.int = TRUE, color = 'mediumorchid4',
          cor.coef = TRUE, cor.method = "pearson",
          xlab = "PHQ9 Row Factor Scores Comp 1", ylab = "Beck Row Factor Scores Comp 1")
PHQ9BeckScatter

#PHQ9 and SAM Episodic correlation of Row Factor Scores of comp 1
PHQ9SAMEpisodic <- cbind(data.frame(resRGCCA$Y[[1]][,1]), data.frame(resRGCCA$Y[[3]][,1]))
colnames(PHQ9SAMEpisodic) <- c("PHQ9","SAMEpisodic")

PHQ9SAMEpisodicScatter <- ggscatter(PHQ9SAMEpisodic, x = "PHQ9", y = "SAMEpisodic", 
          add = "reg.line", conf.int = TRUE, color = 'mediumorchid4',
          cor.coef = TRUE, cor.method = "pearson",
          xlab = "PHQ9 Row Factor Scores Comp 1", ylab = "SAMEpisodic Row Factor Scores Comp 1")
PHQ9SAMEpisodicScatter

#Beck and SAM Episodic correlation of Row Factor Scores of comp 1
BeckSAMEpisodic <- cbind(data.frame(resRGCCA$Y[[2]][,1]), data.frame(resRGCCA$Y[[3]][,1]))
colnames(BeckSAMEpisodic) <- c("Beck","SAMEpisodic")

BeckSAMEpisodicScatter <- ggscatter(BeckSAMEpisodic, x = "Beck", y = "SAMEpisodic", 
          add = "reg.line", conf.int = TRUE, color = 'mediumorchid4',
          cor.coef = TRUE, cor.method = "pearson",
          xlab = "Beck Row Factor Scores Comp 1", ylab = "SAMEpisodic Row Factor Scores Comp 1")
BeckSAMEpisodicScatter
```
#Factor Scores
```{r}
data.frame(colnames(resRGCCA$Y[[1]]) <- c('V1','V2'))
#PHQ9
my.fi.plotPHQ9 <- createFactorMap(resRGCCA$Y[[1]], # data
                            title = "PHQ9 Factor Scores", # title of the plot
                            axis1 = 1, axis2 = 2, # which component for x and y axes
                            pch = 19, # the shape of the dots (google `pch`)
                            cex = 2, # the size of the dots
                            display.labels = FALSE,
                            text.cex = 2.5, # the size of the text
                            alpha.points = 0.1,
                            col.points = resPCAinferencePHQ9$Fixed.Data$Plotting.Data$fi.col, # color of the dots
                            col.labels = resPCAinferencePHQ9$Fixed.Data$Plotting.Data$fi.col, # color for labels of dots
                            )

VariancePHQ9 <- data.frame(resRGCCA$AVE$AVE_X[[1]])
fi.labelsPHQ9 <- createxyLabels.gen(1,2,
                                    lambda = 0,
                             tau = t(round(VariancePHQ9*100, digits = 2)), #Average explained variance
                             axisName = "Component "
                             )
fi.plotPHQ9 <- my.fi.plotPHQ9$zeMap + fi.labelsPHQ9 # you need this line to be able to save them in the end

# get colors
grp.indPHQ9 <- order(totalscorePHQ9)[!duplicated(sort(totalscorePHQ9))]
grp.colPHQ9 <- resPCAinferencePHQ9$Fixed.Data$Plotting.Data$fi.col[grp.indPHQ9] # get the color
grp.namePHQ9 <- totalscorePHQ9[grp.indPHQ9] # get the corresponding groups
names(grp.colPHQ9) <- grp.namePHQ9
# make group means
group.meanPHQ9 <- aggregate(resRGCCA$Y[[1]],
                     by = list(totalscorePHQ9), # must be a list
                     mean)
# need to format the results from `aggregate` correctly
rownames(group.meanPHQ9) <- group.meanPHQ9[,1] # Use the first column as row names
fi.meanPHQ9 <- group.meanPHQ9[,-1] # Exclude the first column
fi.mean.plotPHQ9 <- createFactorMap(fi.meanPHQ9,
                                alpha.points = 1,
                                alpha.labels = 1,
                                col.points = grp.colPHQ9[rownames(fi.meanPHQ9)],
                                col.labels = grp.colPHQ9[rownames(fi.meanPHQ9)],
                                pch = 17,
                                cex = 3,
                                text.cex = 3)
fi.WithMeanPHQ9 <- my.fi.plotPHQ9$zeMap_background + my.fi.plotPHQ9$zeMap_dots + fi.mean.plotPHQ9$zeMap_dots + fi.mean.plotPHQ9$zeMap_text + fi.labelsPHQ9
fi.WithMeanPHQ9

# Depend on the size of your data, this might take a while
#fi.bootPHQ9 <- Boot4Mean(resRGCCA$Y[[1]],
                     #design = totalscorePHQ9,
                     #niter = 1000)

# Check other parameters you can change for this function
#bootCI4meanPHQ9 <- MakeCIEllipses(fi.bootPHQ9$BootCube[,c(1:2),], # get the first two components
                              #col = grp.colPHQ9[rownames(fi.meanPHQ9)])

#fi.WithMeanCIPHQ9 <- my.fi.plotPHQ9$zeMap_background + bootCI4meanPHQ9 + my.fi.plotPHQ9$zeMap_dots + #fi.mean.plotPHQ9$zeMap_dots + fi.mean.plotPHQ9$zeMap_text + fi.labelsPHQ9
#fi.WithMeanCIPHQ9
######################################################################################################
#Beck
my.fi.plotBeck <- createFactorMap(resRGCCA$Y[[2]], # data
                            title = "Beck Factor Scores", # title of the plot
                            axis1 = 1, axis2 = 2, # which component for x and y axes
                            pch = 19, # the shape of the dots (google `pch`)
                            cex = 2, # the size of the dots
                            display.labels = FALSE,
                            text.cex = 2.5, # the size of the text
                            alpha.points = 0.1,
                            col.points = resPCAinferenceBeck$Fixed.Data$Plotting.Data$fi.col, # color of the dots
                            col.labels = resPCAinferenceBeck$Fixed.Data$Plotting.Data$fi.col, # color for labels of dots
                            )

VarianceBeck <- data.frame(resRGCCA$AVE$AVE_X[[2]])
fi.labelsBeck <- createxyLabels.gen(1,2,
                                    lambda = 0,
                             tau = t(round(VarianceBeck*100, digits = 2)), #average explained variance
                             axisName = "Component "
                             )
fi.plotBeck <- my.fi.plotBeck$zeMap + fi.labelsBeck # you need this line to be able to save them in the end

# get colors
grp.indBeck <- order(totalscoreBeck)[!duplicated(sort(totalscoreBeck))]
grp.colBeck <- resPCAinferenceBeck$Fixed.Data$Plotting.Data$fi.col[grp.indBeck] # get the color
grp.nameBeck <- totalscoreBeck[grp.indBeck] # get the corresponding groups
names(grp.colBeck) <- grp.nameBeck
# make group means
group.meanBeck <- aggregate(resRGCCA$Y[[2]],
                     by = list(totalscoreBeck), # must be a list
                     mean)
# need to format the results from `aggregate` correctly
rownames(group.meanBeck) <- group.meanBeck[,1] # Use the first column as row names
fi.meanBeck <- group.meanBeck[,-1] # Exclude the first column
fi.mean.plotBeck <- createFactorMap(fi.meanBeck,
                                alpha.points = 1,
                                alpha.labels = 1,
                                col.points = grp.colBeck[rownames(fi.meanBeck)],
                                col.labels = grp.colBeck[rownames(fi.meanBeck)],
                                pch = 17,
                                cex = 3,
                                text.cex = 3)
fi.WithMeanBeck <- my.fi.plotBeck$zeMap_background + my.fi.plotBeck$zeMap_dots + fi.mean.plotBeck$zeMap_dots + fi.mean.plotBeck$zeMap_text + fi.labelsBeck
fi.WithMeanBeck

#resRGCCA.plot2 <- createFactorMap(resRGCCA$Y[[2]], display.labels = FALSE)
#resRGCCA.plot2 <- resRGCCA.plot2$zeMap + resRGCCA.plot2$zeMap_dots
#resRGCCA.plot2
######################################################################################################
#SAM Episodic
my.fi.plotSAM <- createFactorMap(resRGCCA$Y[[3]], # data
                            title = "SAM Episodic Factor Scores", # title of the plot
                            axis1 = 1, axis2 = 2, # which component for x and y axes
                            pch = 19, # the shape of the dots (google `pch`)
                            cex = 2, # the size of the dots
                            display.labels = FALSE,
                            text.cex = 2.5, # the size of the text
                            alpha.points = 0.1,
                            col.points = resPCAinferenceSAMEpisodic$Fixed.Data$Plotting.Data$fi.col, # color of the dots
                            col.labels = resPCAinferenceSAMEpisodic$Fixed.Data$Plotting.Data$fi.col, # color for labels of dots
                            )

VarianceSAM <- data.frame(resRGCCA$AVE$AVE_X[[3]])
fi.labelsSAM <- createxyLabels.gen(1,2,
                                    lambda = 0,
                             tau = t(round(VarianceSAM*100, digits = 2)),
                             axisName = "Component "
                             )
fi.plotSAM <- my.fi.plotSAM$zeMap + fi.labelsSAM # you need this line to be able to save them in the end
fi.plotSAM

#resRGCCA.plot3 <- createFactorMap(resRGCCA$Y[[3]], display.labels = FALSE)
#resRGCCA.plot3 <- resRGCCA.plot3$zeMap + resRGCCA.plot3$zeMap_dots
#resRGCCA.plot3
```


#Loadings
```{r}
colorsPHQ9 <- prettyGraphsColorSelection(n.colors = nrow(resRGCCA$astar[[1]]))
#PHQ9
my.load.plotPHQ9 <- createFactorMap(resRGCCA$astar[[1]], # data
                            title = "PHQ9 Loadings", # title of the plot
                            axis1 = 1, axis2 = 2, # which component for x and y axes
                            pch = 19, # the shape of the dots (google `pch`)
                            cex = 2, # the size of the dots
                            display.labels = TRUE,
                            text.cex = 2.5, # the size of the text
                            alpha.points = 0.3,
                            col.points = colorsPHQ9, # color of the dots
                            col.labels = colorsPHQ9, # color for labels of dots
                            )

VariancePHQ9 <- data.frame(resRGCCA$AVE$AVE_X[[1]])
load.labelsPHQ9 <- createxyLabels.gen(1,2,
                                    lambda = 0,
                             tau = t(round(VariancePHQ9*100, digits = 2)),
                             axisName = "Component "
                             )
load.plotPHQ9 <- my.load.plotPHQ9$zeMap + load.labelsPHQ9 # you need this line to be able to save them in the end
load.plotPHQ9

#resRGCCA.plot1 <- createFactorMap(resRGCCA$astar[[1]], display.labels = TRUE)
#resRGCCA.plot1 <- resRGCCA.plot1$zeMap + resRGCCA.plot1$zeMap_dots
#resRGCCA.plot1
######################################################################################################
colorsBeck <- prettyGraphsColorSelection(n.colors = nrow(resRGCCA$astar[[2]]))
#Beck
my.load.plotBeck <- createFactorMap(resRGCCA$astar[[2]], # data
                            title = "Beck Loadings", # title of the plot
                            axis1 = 1, axis2 = 2, # which component for x and y axes
                            pch = 19, # the shape of the dots (google `pch`)
                            cex = 2, # the size of the dots
                            display.labels = TRUE,
                            text.cex = 2.5, # the size of the text
                            alpha.points = 0.3,
                            col.points = colorsBeck, # color of the dots
                            col.labels = colorsBeck, # color for labels of dots
                            )

VarianceBeck <- data.frame(resRGCCA$AVE$AVE_X[[2]])
load.labelsBeck <- createxyLabels.gen(1,2,
                                    lambda = 0,
                             tau = t(round(VarianceBeck*100, digits = 2)),
                             axisName = "Component "
                             )
load.plotBeck <- my.load.plotBeck$zeMap + load.labelsBeck # you need this line to be able to save them in the end
load.plotBeck

#resRGCCA.plot2 <- createFactorMap(resRGCCA$astar[[2]], display.labels = TRUE)
#resRGCCA.plot2 <- resRGCCA.plot2$zeMap + resRGCCA.plot2$zeMap_dots
#resRGCCA.plot2
######################################################################################################
colorsSAM <- prettyGraphsColorSelection(n.colors = nrow(resRGCCA$astar[[3]]))
#SAM Episodic
my.load.plotSAM <- createFactorMap(resRGCCA$astar[[3]], # data
                            title = "SAM Episodic Loadings", # title of the plot
                            axis1 = 1, axis2 = 2, # which component for x and y axes
                            pch = 19, # the shape of the dots (google `pch`)
                            cex = 2, # the size of the dots
                            display.labels = TRUE,
                            text.cex = 2.5, # the size of the text
                            alpha.points = 0.3,
                            col.points = colorsSAM, # color of the dots
                            col.labels = colorsSAM, # color for labels of dots
                            )

VarianceSAM <- data.frame(resRGCCA$AVE$AVE_X[[3]])
load.labelsSAM <- createxyLabels.gen(1,2,
                                    lambda = 0,
                             tau = t(round(VarianceSAM*100, digits = 2)),
                             axisName = "Component "
                             )
load.plotSAM <- my.load.plotSAM$zeMap + load.labelsSAM # you need this line to be able to save them in the end
load.plotSAM


#resRGCCA.plot3 <- createFactorMap(resRGCCA$astar[[3]], display.labels = TRUE)
#resRGCCA.plot3 <- resRGCCA.plot3$zeMap + resRGCCA.plot3$zeMap_dots
#resRGCCA.plot3
```

#Average Explained Variance of the Model and Blocks
```{r}
resRGCCA$AVE$AVE_outer_model #average variance explained by design

resRGCCA$AVE$AVE_inner_model #average variacne explained by each block 
```




